---
title: "PM2.5 Analysis for May 2017-2020 BAU v.s. COVID"
author: "Henry Perillo"
date: "6/23/2020"
output: html_document
---

This markdown file details the in-depth analysis of the air quality data for PM2.5 duing the COVID-19 lockdown to draw conclusions about air quality change in the surrounding area during the pandemic.

# Data Input 

First, library the necessary packages:
```{r message = FALSE, warning = FALSE}
# Clear working environment.
rm(list = ls())

# Load Packages.
library(dplyr)
library(plyr)
library(readr)
library(Hmisc)
library(psych)
library(rmweather)
library(ranger)
library(hexbin)
library(tidyr)
library(stringr)
library(ggplot2)
library(data.table)
library(lubridate)
library(Rmisc)
library(knitr)
```

Call file:
```{r message = FALSE, warning = FALSE}
# Set working directory.
setwd("~/Documents/MSc_ES_AQ_Research_Project/Data/AQ/Final_Data")

# Load data from master files. 
pm_1 <- read_csv('PM1718.csv')
pm_1 <- pm_1[,-5]
pm_2 <- read_csv('PM1920.csv')
```

Edit dataframe: 
```{r message = FALSE, warning = FALSE}
# We're left with a dataframe containing daily PM 
# values in PM_1 and hourly PM values in PM_2. Now, 
# let's isolate the columns of interest.
PM_2 <- pm_2 %>%
  dplyr::rename(`Rathmines (U-B)` = `Rathmines`,
         `Marino (S-B)` = `Marino`,
         `Finglas (S-B)` = `Finglas`,
         `Ringsend (U-T)` = `Ringsend`)
PM_2 <- PM_2 %>%
		gather("Rathmines (U-B)", "Marino (S-B)", "Finglas (S-B)", "Ringsend (U-T)", key = 'Station', value = 'value')

# We can now convert the date and time column to a timestamp 
# format so we can use it with the rmweather package. Also, 
# we'll create year, day, hour, and month columns to house 
# that data individually should we choose to break up the 
# master dataframe later. 
PM_2$date <- dmy_hm(PM_2$date)

# Create Year, Month, Date, and Hour columns.
PM_2 <- PM_2 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

# We'll make all of our data numerical.
PM_2 <- PM_2 %>%
  mutate(value = as.numeric(value))
```

```{r message = FALSE, warning = FALSE}
# Convert relevant columns to the correct format. 
pm_1$date <- dmy(pm_1$date)
pm_2$date <- dmy_hm(pm_2$date)
pm_2 <- pm_2[,-5]

# Create Year, Month, Date, and Hour columns.
pm_1 <- pm_1 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10))
pm_2 <- pm_2 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

# Make 'Month' data numerical.
pm_1$Finglas <- as.numeric(pm_1$Finglas)
pm_1$Marino <- as.numeric(pm_1$Marino)
pm_1$Rathmines <- as.numeric(pm_1$Rathmines)
pm_2$Finglas <- as.numeric(pm_2$Finglas)
pm_2$Marino <- as.numeric(pm_2$Marino)
pm_2$Rathmines <- as.numeric(pm_2$Rathmines)

# Remove NA values.
pm_1 <- pm_1[!is.na(pm_1$Rathmines), ]
pm_1 <- pm_1[!is.na(pm_1$Finglas), ]
pm_1 <- pm_1[!is.na(pm_1$Marino), ]
pm_2 <- pm_2[!is.na(pm_2$Rathmines), ]
pm_2 <- pm_2[!is.na(pm_2$Finglas), ]
pm_2 <- pm_2[!is.na(pm_2$Marino), ]

# Remove negative values.
pm_2 <- pm_2 %>%
  filter(Rathmines >= 0,
         Finglas >= 0,
         Marino >= 0)

# Create summary values.
pm_2 <- pm_2 %>%
  group_by(Year, Month, Date) %>%
  dplyr::summarize(Finglas = mean(Finglas),
                   Marino = mean(Marino),
                   Rathmines = mean(Rathmines))

# Remove extraneous columns.
pm_1 <- pm_1[,-1]
pm_1 <- pm_1[,c(4,5,6,1,2,3)]

# Filter for May.
pm_1 <- pm_1 %>%
  filter(Month == '05')
pm_2 <- pm_2 %>%
  filter(Month == '05')

# Joing columns. 
PM <- dplyr::bind_rows(pm_1, pm_2)
```

The result is a cleaner dataframe that holds daily air quality data at three monitoring stations in the GDA from 2017 to 2020. 

```{r message = FALSE, warning = FALSE}
PM_1 <- PM %>%
  dplyr::rename(`Rathmines (U-B)` = `Rathmines`,
         `Marino (S-B)` = `Marino`,
         `Finglas (S-B)` = `Finglas`)
PM_1 <- PM_1 %>%
		gather("Rathmines (U-B)", "Marino (S-B)", "Finglas (S-B)", key = 'Station', value = 'value')

May_Monthly_Avgs_PM <- summarySE(PM_1, measurevar= "value", groupvars=c('Station', "Month", "Year"))
```


Let's now check the residuals for normality. 

Residuals for Rathmines:
```{r message = FALSE, warning = FALSE} 
# Build the linear model.
May_Rath_PM.lm <- lm(Rathmines ~ Year, data = PM)

# Create a QQ plot of residuals.
qqnorm(residuals(May_Rath_PM.lm))
qqline(residuals(May_Rath_PM.lm), col = "red")

# Shapiro-wilk test.
shapiro.test(residuals(May_Rath_PM.lm))
```

Residuals for Marino
```{r message = FALSE, warning = FALSE}
# Build the linear model.
May_Mar_PM.lm <- lm(`Marino` ~ Year, data = PM)

# Create a QQ plot of residuals.
qqnorm(residuals(May_Mar_PM.lm))
qqline(residuals(May_Mar_PM.lm), col = "red")

# Shapiro-wilk test.
shapiro.test(residuals(May_Mar_PM.lm))
```

Residuals for Finglas
```{r message = FALSE, warning = FALSE}
# Build the linear model.
May_Fin_PM.lm <- lm(`Finglas` ~ Year, data = PM)

# Create a QQ plot of residuals.
qqnorm(residuals(May_Fin_PM.lm))
qqline(residuals(May_Fin_PM.lm), col = "red")

# Shapiro-wilk test.
shapiro.test(residuals(May_Fin_PM.lm))
```

## Monthly

May monthly multiplot:
```{r message = FALSE, warning = FALSE}
# Barplot.
May_Monthly_PM_plot <- ggplot(May_Monthly_Avgs_PM, aes(x=Year, y=value)) + 
  geom_point(stat="identity",
             size=1) +      # Thinner lines
  geom_errorbar(aes(ymin=value-se, ymax=value+se),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Year',
       y = 'Monthly Avg [PM] µg/m^3',
       color = "Year",
       title = "PM2.5 BAU Averages vs. COVID Average",
       subtitle = "May") + 
  theme_bw()+
  facet_wrap(~ Station, dir = 'v')+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12))
May_Monthly_PM_plot
```

Create separate dataframes for each monitoring station: 
```{r message = FALSE, warning = FALSE}
# Dataframe by station.
Rath_Monthly_Avgs_May_PM <- PM_1 %>%
  filter(Station == "Rathmines (U-B)")
Fin_Monthly_Avgs_May_PM <- PM_1 %>%
  filter(Station == "Finglas (S-B)")
Mar_Monthly_Avgs_May_PM <- PM_1 %>%
  filter(Station == "Marino (S-B)")

# Kruskall-wallis test for Rathmines.
May_Rath.w <- kruskal.test(value ~ Year, data = Rath_Monthly_Avgs_May_PM)
May_Rath.w
pairwise.wilcox.test(Rath_Monthly_Avgs_May_PM$value, Rath_Monthly_Avgs_May_PM$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Marino.
May_Mar.w <- kruskal.test(value ~ Year, data = Mar_Monthly_Avgs_May_PM)
May_Mar.w
pairwise.wilcox.test(Mar_Monthly_Avgs_May_PM$value, Mar_Monthly_Avgs_May_PM$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Finglas.
May_Fin.w <- kruskal.test(value ~ Year, data = Fin_Monthly_Avgs_May_PM)
May_Fin.w
pairwise.wilcox.test(Fin_Monthly_Avgs_May_PM$value, Fin_Monthly_Avgs_May_PM$Year,
                 p.adjust.method = "BH")
```
