---
title: "NO2 Analysis for May 2017-2020 BAU v.s. COVID"
author: "Henry Perillo"
date: "6/23/2020"
output: html_document
---

This markdown file details the in-depth analysis of the air quality data for Rathmines monitoring station (classification = urban) duing the COVID-19 lockdown to draw conclusions about air quality change in the surrounding area during the pandemic.

# Data Input 

First, library the necessary packages:
```{r message = FALSE, warning = FALSE}
# Clear working environment
rm(list = ls())

# Load Packages
library(dplyr)
library(plyr)
library(readr)
library(Hmisc)
library(psych)
library(rmweather)
library(ranger)
library(hexbin)
library(tidyr)
library(stringr)
library(ggplot2)
library(data.table)
library(lubridate)
library(Rmisc)
library(knitr)
```

Call file:
```{r message = FALSE, warning = FALSE}
# Set working directory.
setwd("~/Documents/MSc_ES_AQ_Research_Project/Data/AQ/Final_Data")
# Load data from master file for 2017-2020. 
no2 <- read_csv('NO2.csv')
```

Edit dataframe: 
```{r message = FALSE, warning = FALSE}
# We're left with a dataframe containing hourly NO2 values.
# Now, let's isolate the columns of interest.
no2 <- no2[,-3]
NO2 <- no2 %>%
  dplyr::rename(`Rathmines (U-B)` = `Rathmines`,
         `Winetavern Street (U-B)` = `Winetavern Street`,
         `Dun Laoghaire (S-B)` = `Dun Laoghaire`)
NO2 <- NO2 %>%
		gather("Rathmines (U-B)", "Winetavern Street (U-B)", "Dun Laoghaire (S-B)", key = 'Station', value = 'value')

# We can now convert the date and time column to a timestamp 
# format so we can use it with the rmweather package. Also, 
# we'll create year, day, hour, and month columns to house 
# that data individually should we choose to break up the 
# master dataframe later. 
NO2$date <- dmy_hm(NO2$date)

# Create Year, Month, Date, and Hour columns.
NO2 <- NO2 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

# We'll make all of our data numerical:
NO2 <- NO2 %>%
  mutate(value = as.numeric(value))
```

The result is a cleaner dataframe that holds air quality data at three monitoring stations in the GDA from 2017 to 2020. 

Create linear dataframe. 
```{r message = FALSE, warning = FALSE}
# Use rmweather to create a dataframe with 'weekday' column. 
# Also removes the 'Na' values.
NO2 <- NO2 %>% 
  rmw_prepare_data(na.rm = TRUE)

# Remove negative values
NO2 <- NO2 %>%
  filter(value >= 0)

# Make 'Month' data numerical
NO2$Month <- as.numeric(NO2$Month)

# Filter months
COVID_Linear <- NO2%>%
  filter(Month < 7)

# Create new dataframe with summary values for each variable
COVID_Linear_Daily <- summarySE(COVID_Linear, measurevar= "value", groupvars=c('Station', "Month", "Year", 'Date'))

# Add an ID column for weeks to enable gtrouping later
COVID_Linear_Daily <- COVID_Linear_Daily %>%
  mutate(Week = case_when(
    Date >= '01' & Date <= '07' ~ 1,
    Date >= '08' & Date <= '14' ~ 2,
    Date >= '15' & Date <= '21'  ~ 3,
    Date >= '22' & Date <= '31' ~ 4))
```

Examine monthly averages: 
```{r message = FALSE, warning = FALSE}
# Create monthly summary dataframe
Monthly_Avgs_NO2 <- summarySE(COVID_Linear_Daily, measurevar= "value", groupvars=c('Station', "Month", "Year"))

# Make month column numerical
Monthly_Avgs_NO2$Month <- as.numeric(Monthly_Avgs_NO2$Month)

# Isolate May
May_Monthly_Avgs_NO2 <- Monthly_Avgs_NO2 %>%
  filter(Month == 5)
```

Check the residuals for normality:
```{r message = FALSE, warning = FALSE}
# Create the residuals dataframe:
no2$date <- dmy_hm(no2$date)

# We'll make all of our data numerical:
no2 <- no2 %>%
  mutate(Rathmines = as.numeric(Rathmines),
         `Dun Laoghaire` = as.numeric(`Dun Laoghaire`),
         `Winetavern Street` = as.numeric(`Winetavern Street`))

# Remove NA values.
no2 <- no2[!is.na(no2$Rathmines), ]
no2 <- no2[!is.na(no2$`Winetavern Street`), ]
no2 <- no2[!is.na(no2$`Dun Laoghaire`), ]

# Remove negative values.
no2 <- no2 %>%
  filter(Rathmines >= 0,
         `Winetavern Street` >= 0,
         `Dun Laoghaire` >= 0)

# Create Year, Month, Date, and Hour columns.
no2 <- no2 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

May_NO2 <- no2 %>%
  filter(Month == '05')
```

Residuals for Rathmines:
```{r}
# Build the linear model.
May_Rath_NO2.lm <- lm(Rathmines ~ Year, data = May_NO2)

# Create a QQ plot of residuals.
qqnorm(residuals(May_Rath_NO2.lm))
qqline(residuals(May_Rath_NO2.lm), col = "red")

# Shapiro-wilk test.
shapiro.test(residuals(May_Rath_NO2.lm))
```

Residuals for Winetavern Street
```{r message = FALSE, warning = FALSE}
# Build the linear model.
May_Wine_NO2.lm <- lm(`Winetavern Street` ~ Year, data = May_NO2)

# Create a QQ plot of residuals.
qqnorm(residuals(May_Wine_NO2.lm))
qqline(residuals(May_Wine_NO2.lm), col = "red")

# Shapiro-wilk test.
shapiro.test(residuals(May_Wine_NO2.lm))
```

Residuals for Dun Laoghaire
```{r message = FALSE, warning = FALSE}
# Build the linear model.
May_Dun_NO2.lm <- lm(`Dun Laoghaire` ~ Year, data = May_NO2)

# Create a QQ plot of residuals.
qqnorm(residuals(May_Dun_NO2.lm))
qqline(residuals(May_Dun_NO2.lm), col = "red")

# Shapiro-wilk test.
shapiro.test(residuals(May_Dun_NO2.lm))
```

## Monthly averages:

May monthly multiplot:
```{r message = FALSE, warning = FALSE}
# Barplot.
May_Monthly_NO2_plot <- ggplot(May_Monthly_Avgs_NO2, aes(x=Year, y=value)) + 
  geom_point(stat="identity",
             size=1) +      # Thinner lines
  geom_errorbar(aes(ymin=value-se, ymax=value+se),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Year',
       y = 'Monthly Avg [NO2] µg/m^3',
       color = "Year",
       title = "NO2 BAU Averages vs. COVID Average",
       subtitle = "May") + 
  theme_bw()+
  facet_wrap(~ Station, dir = 'v')+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12))
May_Monthly_NO2_plot
```

Create separate dataframes for each monitoring station: 
```{r message = FALSE, warning = FALSE}
# Dataframe by station.
Rath_Monthly_Avgs_May_NO2 <- COVID_Linear_Daily %>%
  filter(Station == "Rathmines (U-B)",
         Month == 5)
Dun_Monthly_Avgs_May_NO2 <- COVID_Linear_Daily %>%
  filter(Station == "Dun Laoghaire (S-B)",
         Month == 5)
Wine_Monthly_Avgs_May_NO2 <- COVID_Linear_Daily %>%
  filter(Station == "Winetavern Street (U-B)",
         Month == 5)

# Kruskall-wallis test for Rathmines.
May_Rath.w <- kruskal.test(value ~ Year, data = Rath_Monthly_Avgs_May_NO2)
pairwise.wilcox.test(Rath_Monthly_Avgs_May_NO2$value, Rath_Monthly_Avgs_May_NO2$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Winetavern Street.
May_Wine.w <- kruskal.test(value ~ Year, data = Wine_Monthly_Avgs_May_NO2)
pairwise.wilcox.test(Wine_Monthly_Avgs_May_NO2$value, Wine_Monthly_Avgs_May_NO2$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Dun laoghaire.
May_Dun.w <- kruskal.test(value ~ Year, data = Dun_Monthly_Avgs_May_NO2)
pairwise.wilcox.test(Dun_Monthly_Avgs_May_NO2$value, Dun_Monthly_Avgs_May_NO2$Year,
                 p.adjust.method = "BH")
```
