---
title: "May PM2.5 Data Analysis - Panels by Station"
author: "Henry Perillo"
date: "6/23/2020"
output: html_document
---

This markdown file details the in-depth analysis of the air quality data for PM2.5 duing the COVID-19 lockdown to draw conclusions about air quality change in the surrounding area during the pandemic.

# Data Input 

First, library the necessary packages:
```{r message = FALSE, warning = FALSE}
# Clear working environment
rm(list = ls())

# Load Packages
library(dplyr)
library(plyr)
library(readr)
library(Hmisc)
library(psych)
library(rmweather)
library(ranger)
library(hexbin)
library(tidyr)
library(stringr)
library(ggplot2)
library(data.table)
library(lubridate)
library(Rmisc)
library(knitr)
```

Call file:
```{r message = FALSE, warning = FALSE}
# Set working directory
setwd("~/Documents/MSc_ES_AQ_Research_Project/Data/AQ/Final_Data")

# Load data from master file
pm_1 <- read_csv('PM1718.csv')
pm_1 <- pm_1[,-5]
pm_2 <- read_csv('PM1920.csv')
```

Edit dataframe: 
```{r message = FALSE, warning = FALSE}
# We're left with a dataframe containing daily PM values in PM_1 and hourly PM values in PM_2. Now, let's isolate the columns of interest.
PM_2 <- pm_2 %>%
  dplyr::rename(`Rathmines (U-B)` = `Rathmines`,
         `Marino (S-B)` = `Marino`,
         `Finglas (S-B)` = `Finglas`,
         `Ringsend (U-T)` = `Ringsend`)
PM_2 <- PM_2 %>%
		gather("Rathmines (U-B)", "Marino (S-B)", "Finglas (S-B)", "Ringsend (U-T)", key = 'Station', value = 'value')

# We can now convert the date and time column to a timestamp 
# format so we can use it with the rmweather package. Also, 
# we'll create year, day, hour, and month columns to house 
# that data individually should we choose to break up the 
# master dataframe later. 
PM_2$date <- dmy_hm(PM_2$date)

# Create Year, Month, Date, and Hour columns.
PM_2 <- PM_2 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

# We'll make all of our data numerical:
PM_2 <- PM_2 %>%
  mutate(value = as.numeric(value))
```


```{r message = FALSE, warning = FALSE}
pm_1$date <- dmy(pm_1$date)
pm_2$date <- dmy_hm(pm_2$date)
pm_2 <- pm_2[,-5]

# Create Year, Month, Date, and Hour columns.
pm_1 <- pm_1 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10))
pm_2 <- pm_2 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

# Make 'Month' data numerical
pm_1$Finglas <- as.numeric(pm_1$Finglas)
pm_1$Marino <- as.numeric(pm_1$Marino)
pm_1$Rathmines <- as.numeric(pm_1$Rathmines)
pm_2$Finglas <- as.numeric(pm_2$Finglas)
pm_2$Marino <- as.numeric(pm_2$Marino)
pm_2$Rathmines <- as.numeric(pm_2$Rathmines)

# Remove NA values
pm_1 <- pm_1[!is.na(pm_1$Rathmines), ]
pm_1 <- pm_1[!is.na(pm_1$Finglas), ]
pm_1 <- pm_1[!is.na(pm_1$Marino), ]
pm_2 <- pm_2[!is.na(pm_2$Rathmines), ]
pm_2 <- pm_2[!is.na(pm_2$Finglas), ]
pm_2 <- pm_2[!is.na(pm_2$Marino), ]

# Remove negative values
pm_2 <- pm_2 %>%
  filter(Rathmines >= 0,
         Finglas >= 0,
         Marino >= 0)

pm_2 <- pm_2 %>%
  group_by(Year, Month, Date) %>%
  dplyr::summarize(Finglas = mean(Finglas),
                   Marino = mean(Marino),
                   Rathmines = mean(Rathmines))

pm_1 <- pm_1[,-1]
pm_1 <- pm_1[,c(4,5,6,1,2,3)]

pm_1 <- pm_1 %>%
  filter(Month == '05')
pm_2 <- pm_2 %>%
  filter(Month == '05')

PM <- dplyr::bind_rows(pm_1, pm_2)
```

The result is a cleaner dataframe that holds daily air quality data at three monitoring stations in the GDA from 2017 to 2020. 

```{r message = FALSE, warning = FALSE}
PM_1 <- PM %>%
  dplyr::rename(`Rathmines (U-B)` = `Rathmines`,
         `Marino (S-B)` = `Marino`,
         `Finglas (S-B)` = `Finglas`)
PM_1 <- PM_1 %>%
		gather("Rathmines (U-B)", "Marino (S-B)", "Finglas (S-B)", key = 'Station', value = 'value')

May_Monthly_Avgs_PM <- summarySE(PM_1, measurevar= "value", groupvars=c('Station', "Month", "Year"))
```


Let's now check the residuals for normality. 

Residuals for Rathmines:
```{r message = FALSE, warning = FALSE} 
# Build the linear model
May_Rath_PM.lm <- lm(Rathmines ~ Year, data = PM)

# Create a QQ plot of residuals
qqnorm(residuals(May_Rath_PM.lm))
qqline(residuals(May_Rath_PM.lm), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(May_Rath_PM.lm))
```

Residuals for Marino
```{r message = FALSE, warning = FALSE}
# Build the linear model
May_Mar_PM.lm <- lm(`Marino` ~ Year, data = PM)

# Create a QQ plot of residuals
qqnorm(residuals(May_Mar_PM.lm))
qqline(residuals(May_Mar_PM.lm), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(May_Mar_PM.lm))
```

Residuals for Finglas
```{r message = FALSE, warning = FALSE}
# Build the linear model
May_Fin_PM.lm <- lm(`Finglas` ~ Year, data = PM)

# Create a QQ plot of residuals
qqnorm(residuals(May_Fin_PM.lm))
qqline(residuals(May_Fin_PM.lm), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(May_Fin_PM.lm))
```

## Monthly

May monthly multiplot:
```{r message = FALSE, warning = FALSE}
# Barplot
May_Monthly_PM_plot <- ggplot(May_Monthly_Avgs_PM, aes(x=Year, y=value)) + 
  geom_point(stat="identity",
             size=1) +      # Thinner lines
  geom_errorbar(aes(ymin=value-se, ymax=value+se),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Year',
       y = 'Monthly Avg [PM] µg/m^3',
       color = "Year",
       title = "PM2.5 BAU Averages vs. COVID Average",
       subtitle = "May") + 
  theme_bw()+
  facet_wrap(~ Station, dir = 'v')+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12))
May_Monthly_PM_plot
```

Create separate dataframes for each monitoring station: 
```{r message = FALSE, warning = FALSE}
# Dataframe by station
Rath_Monthly_Avgs_May_PM <- PM_1 %>%
  filter(Station == "Rathmines (U-B)")
Fin_Monthly_Avgs_May_PM <- PM_1 %>%
  filter(Station == "Finglas (S-B)")
Mar_Monthly_Avgs_May_PM <- PM_1 %>%
  filter(Station == "Marino (S-B)")

# Kruskall-wallis test for Rathmines
May_Rath.w <- kruskal.test(value ~ Year, data = Rath_Monthly_Avgs_May_PM)
May_Rath.w
pairwise.wilcox.test(Rath_Monthly_Avgs_May_PM$value, Rath_Monthly_Avgs_May_PM$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Marino
May_Mar.w <- kruskal.test(value ~ Year, data = Mar_Monthly_Avgs_May_PM)
May_Mar.w
pairwise.wilcox.test(Mar_Monthly_Avgs_May_PM$value, Mar_Monthly_Avgs_May_PM$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Finglas
May_Fin.w <- kruskal.test(value ~ Year, data = Fin_Monthly_Avgs_May_PM)
May_Fin.w
pairwise.wilcox.test(Fin_Monthly_Avgs_May_PM$value, Fin_Monthly_Avgs_May_PM$Year,
                 p.adjust.method = "BH")
```
## Weekly

Weekly dataframe:
```{r message = FALSE, warning = FALSE}
# Add an ID column for weeks to enable gtrouping later
PM_1 <- PM_1 %>%
  mutate(Week = case_when(
    Date >= '01' & Date <= '07' ~ 1,
    Date >= '08' & Date <= '14' ~ 2,
    Date >= '15' & Date <= '21'  ~ 3,
    Date >= '22' & Date <= '31' ~ 4))

# Summary dataframe
Weekly_Avgs_PM <- summarySE(PM_1, measurevar= "value", groupvars=c('Station', "Month", "Week", "Year"))

# Make the 'Week' column numerical
Weekly_Avgs_PM$Week <- as.numeric(Weekly_Avgs_PM$Week)
```

May weekly multiplot:
```{r message = FALSE, warning = FALSE}
# Line plot for weeks
May_Weekly_PM_plot <- ggplot(data = Weekly_Avgs_PM, aes(x = Week, y = value)) +
  geom_line(aes(color = Year)) + 
  geom_errorbar(aes(ymin=value-se, ymax=value+se, color = Year),
                size=.3,    # Thinner lines
                width=.2) +
  labs(x = 'Week',
       y = 'Weekly Avg [PM] µg/m^3',
       color = "Year",
       title = "Weekly PM Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0))
  )
May_Weekly_PM_plot
```

## Daily

Daily averages: 
```{r message = FALSE, warning = FALSE}
# Make 'Date' column numeric
PM_1$Date <- as.numeric(PM_1$Date)
```

Daily multiplot:
```{r message = FALSE, warning = FALSE}
# Line plot for days
May_Daily_PM_plot <- ggplot(data = PM_1, aes(x = Date, y = value)) +
  geom_line(aes(color = Year)) + 
  labs(x = 'Date',
       y = 'Daily Avg [PM] µg/m^3',
       color = "Year",
       title = "Daily PM Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0))
  )
May_Daily_PM_plot
```

## Diurnal Analysis

Diurnal weekday analysis:
```{r message = FALSE, warning = FALSE}
PM_2 <- PM_2 %>% 
  rmw_prepare_data(na.rm = TRUE)

# Create weekday dataframe
COVID_Linear_weekday <- PM_2 %>%
  filter(weekday >= 1,
         weekday < 6)

# Remove NA values
COVID_Linear_weekday <- COVID_Linear_weekday[!is.na(COVID_Linear_weekday$value), ]

# Remove negative values
COVID_Linear_weekday <- COVID_Linear_weekday %>%
  filter(value >= 0)

# Make 'Year' column a factor
COVID_Linear_weekday$Year <- as.factor(COVID_Linear_weekday$Year)

# Create the two-year average values to compare to the COVID experimental period value. 
COVID_Linear_weekday <- COVID_Linear_weekday %>%
  mutate(Period = case_when(
    Year == '19'~ '2019',
    Year == '20' ~ '2020'))
```

Diurnal weekday averages by year:
```{r message = FALSE, warning = FALSE}
# Weekday summary dataframe
Weekday_Diurnal_Avgs_PM <- summarySE(COVID_Linear_weekday, measurevar= "value", groupvars=c('Station', "Year", "Month", "Hour" ))

# Make 'Year' column a factor
Weekday_Diurnal_Avgs_PM$Year <- as.factor(Weekday_Diurnal_Avgs_PM$Year)

# Isolate May
May_weekday_Diurnal_Avgs_PM <- Weekday_Diurnal_Avgs_PM %>%
  filter(Month == '05')
```

Diurnal May multiplot weekday:
```{r message = FALSE, warning = FALSE}
# Create separate dataframes for each year
May_weekday_Diurnal_Avgs_PM_19 <- May_weekday_Diurnal_Avgs_PM %>%
  filter(Year == '19')
May_weekday_Diurnal_Avgs_PM_20 <- May_weekday_Diurnal_Avgs_PM %>%
  filter(Year == '20')

# Merge dataframes together
May_weekday_Diurnal_Avgs_PM_19_20 <- cbind(May_weekday_Diurnal_Avgs_PM_19,May_weekday_Diurnal_Avgs_PM_20)
May_weekday_Diurnal_Avgs_PM_19_20 <- May_weekday_Diurnal_Avgs_PM_19_20[,-c(10:14)]

# Calculate avg hourly differences
Hryl_diff_PM_19_20 <- May_weekday_Diurnal_Avgs_PM_19_20 %>%
  mutate(hrly_diff = value-value.1)
write.csv(Hryl_diff_PM_19_20, "~/Desktop/Hryl_diff_PM_19_20_weekday.csv")

Hryl_diff_PM_19_20_sum <- summarySE(Hryl_diff_PM_19_20, measurevar= "hrly_diff", groupvars=c('Station'))

# Line plot of diurnal patterns by year
May_weekday_Diurnal_PM_plot <- ggplot(data = May_weekday_Diurnal_Avgs_PM_19_20, aes(Hour)) +
  geom_line(aes(y = value, group = 1, colour = "2019")) +
  geom_line(aes(y = value.1, group = 1, colour = "2020")) + 
  geom_errorbar(aes(ymin=value-se,
                    ymax=value+se, colour = "2019"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.1-se.1, ymax=value.1+se.1, colour = "2020"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Hour',
       y = 'Hourly Avg [PM] µg/m^3',
       color = "Year",
       title = "Weekday Diurnal PM Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12)
  )
May_weekday_Diurnal_PM_plot
```

Diurnal weekend dataframe:
```{r message = FALSE, warning = FALSE}
# Create weekend dataframe
COVID_Linear_weekend <- PM_2 %>%
  filter(weekday >= 6,
         weekday <= 7)

# Remove NA values
COVID_Linear_weekend <- COVID_Linear_weekend[!is.na(COVID_Linear_weekend$value), ]

# Remove negative values
COVID_Linear_weekend <- COVID_Linear_weekend %>%
  filter(value >= 0)

COVID_Linear_weekend$Year <- as.factor(COVID_Linear_weekend$Year)

# Create the two-year average values to compare to the COVID experimental period value. 
COVID_Linear_weekend <- COVID_Linear_weekend %>%
  mutate(Period = case_when(
    Year == '19'~ '2019',
    Year == '20' ~ '2020'))
```

Diurnal weekend Averages
```{r message = FALSE, warning = FALSE}
# Create summary dataframe
weekend_Diurnal_Avgs_PM <- summarySE(COVID_Linear_weekend, measurevar= "value", groupvars=c('Station', "Year", "Month", "Hour" ))

# Make 'Year' column a factor
weekend_Diurnal_Avgs_PM$Year <- as.factor(weekend_Diurnal_Avgs_PM$Year)

# Separate May
May_weekend_Diurnal_Avgs_PM <- weekend_Diurnal_Avgs_PM %>%
  filter(Month == '05')
```

Diurnal May multiplot weekend:
```{r message = FALSE, warning = FALSE}
# Create separate dataframes for each year
May_weekend_Diurnal_Avgs_PM_19 <- May_weekend_Diurnal_Avgs_PM %>%
  filter(Year == '19')
May_weekend_Diurnal_Avgs_PM_20 <- May_weekend_Diurnal_Avgs_PM %>%
  filter(Year == '20')

# Bind dataframes together
May_weekend_Diurnal_Avgs_PM_19_20 <- cbind( May_weekend_Diurnal_Avgs_PM_19,May_weekend_Diurnal_Avgs_PM_20)

May_weekend_Diurnal_Avgs_PM_19_20 <- May_weekend_Diurnal_Avgs_PM_19_20[,-c(10:14)]

# Calculate avg hourly differences
Hryl_diff_PM_19_20_weekend <- May_weekend_Diurnal_Avgs_PM_19_20 %>%
  mutate(hrly_diff = value-value.1)
write.csv(Hryl_diff_PM_19_20_weekend, "~/Desktop/Hryl_diff_PM_19_20_weekend.csv")

Hryl_diff_PM_19_20_sum_weekend <- summarySE(Hryl_diff_PM_19_20_weekend, measurevar= "hrly_diff", groupvars=c('Station'))

# Line plot of weekend averages
May_weekend_Diurnal_PM_plot <- ggplot(data = May_weekend_Diurnal_Avgs_PM_19_20, aes(Hour)) +
  geom_line(aes(y = value, group = 1, colour = "2019")) +
  geom_line(aes(y = value.1, group = 1, colour = "2020")) +
  geom_errorbar(aes(ymin=value-se,
                    ymax=value+se, colour = "2019"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.1-se.1, ymax=value.1+se.1, colour = "2020"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Hour',
       y = 'Hourly Avg [PM] µg/m^3',
       color = "Year",
       title = "Weekend Diurnal PM Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12)
  )
May_weekend_Diurnal_PM_plot
```
