---
title: "May O3 Data Analysis - Panels by Station"
author: "Henry Perillo"
date: "6/23/2020"
output: html_document
---

This markdown file details the in-depth analysis of the air quality data for Rathmines monitoring station (classification = urban) duing the COVID-19 lockdown to draw conclusions about air quality change in the surrounding area during the pandemic.

# Data Input 

First, library the necessary packages:
```{r message = FALSE, warning = FALSE}
# Clear working environment
rm(list = ls())

# Load Packages
library(dplyr)
library(plyr)
library(readr)
library(Hmisc)
library(psych)
library(rmweather)
library(ranger)
library(hexbin)
library(tidyr)
library(stringr)
library(ggplot2)
library(data.table)
library(lubridate)
library(Rmisc)
library(knitr)
```

Call file:
```{r message = FALSE, warning = FALSE}
# Set working directory
setwd("~/Desktop/Research_Project/Data/AQ/Final_Data")

# Load data from master file
o3 <- read_csv('O3.csv')
```

Edit dataframe: 
```{r message = FALSE, warning = FALSE}
# We're left with a dataframe containing hourly O3 values for
# every day of 2018. Now, let's isolate the columns of interest.
O3 <- o3 %>%
  dplyr::rename(`Rathmines (U-B)` = `Rathmines`,
         `Clonskeagh (S-B)` = `Clonskeagh`,
         `Swords (S-B)` = `Swords`)
O3 <- O3 %>%
		gather("Rathmines (U-B)", "Clonskeagh (S-B)", "Swords (S-B)", key = 'Station', value = 'value')

# We can now convert the date and time column to a timestamp 
# format so we can use it with the rmweather package. Also, 
# we'll create year, day, hour, and month columns to house 
# that data individually should we choose to break up the 
# master dataframe later. 
O3$date <- dmy_hm(O3$date)

# Create Year, Month, Date, and Hour columns.
O3 <- O3 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

# We'll make all of our data numerical:
O3 <- O3 %>%
  mutate(value = as.numeric(value))
```

The result is a cleaner dataframe that holds hourly meteorlogical and air quality data at three monitoring stations in the GDA from 2017 to 2020. 

Create linear dataframe: 
```{r message = FALSE, warning = FALSE}
# Use rmweather to create a dataframe with 'weekday' column
O3 <- O3 %>% 
  rmw_prepare_data(na.rm = TRUE)

# Remove negative values
O3 <- O3 %>%
  filter(value >= 0)

# Make 'Month' data numerical
O3$Month <- as.numeric(O3$Month)

# Filter months
COVID_Linear <- O3%>%
  filter(Month < 7)

# Create new dataframe with summary values for each variable
COVID_Linear_Daily <- summarySE(COVID_Linear, measurevar= "value", groupvars=c('Station', "Month", "Year", 'Date'))

# Add an ID column for weeks to enable gtrouping later
COVID_Linear_Daily <- COVID_Linear_Daily %>%
  mutate(Week = case_when(
    Date >= '01' & Date <= '07' ~ 1,
    Date >= '08' & Date <= '14' ~ 2,
    Date >= '15' & Date <= '21'  ~ 3,
    Date >= '22' & Date <= '31' ~ 4))
```

Examine monthly averages: 
```{r message = FALSE, warning = FALSE}
# Create monthly summary dataframe
Monthly_Avgs_O3 <- summarySE(COVID_Linear_Daily, measurevar= "value", groupvars=c('Station', "Month", "Year"))

# Make month column numerical
Monthly_Avgs_O3$Month <- as.numeric(Monthly_Avgs_O3$Month)

# Isolate May
May_Monthly_Avgs_O3 <- Monthly_Avgs_O3 %>%
  filter(Month == 5)
```

Check the residuals for normality:
```{r message = FALSE, warning = FALSE}
# Create the residuals dataframe:
o3$date <- dmy_hm(o3$date)

# We'll make all of our data numerical:
o3 <- o3 %>%
  mutate(Rathmines = as.numeric(Rathmines),
         `Swords` = as.numeric(`Swords`),
         `Clonskeagh` = as.numeric(`Clonskeagh`))

# Remove NA values
o3 <- o3[!is.na(o3$Rathmines), ]
o3 <- o3[!is.na(o3$`Clonskeagh`), ]
o3 <- o3[!is.na(o3$`Swords`), ]

# Remove negative values
o3 <- o3 %>%
  filter(Rathmines >= 0,
         `Clonskeagh` >= 0,
         `Swords` >= 0)

# Create Year, Month, Date, and Hour columns.
o3 <- o3 %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10),
         Hour = str_sub (date, 12, 13))

May_O3 <- o3 %>%
  filter(Month == '05')
```

Residuals for Rathmines:
```{r}
# Build the linear model
May_Rath_O3.lm <- lm(Rathmines ~ Year, data = May_O3)

# Create a QQ plot of residuals
qqnorm(residuals(May_Rath_O3.lm))
qqline(residuals(May_Rath_O3.lm), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(May_Rath_O3.lm))
```

Residuals for Clonskeagh
```{r message = FALSE, warning = FALSE}
# Build the linear model
May_Clon_O3.lm <- lm(`Clonskeagh` ~ Year, data = May_O3)

# Create a QQ plot of residuals
qqnorm(residuals(May_Clon_O3.lm))
qqline(residuals(May_Clon_O3.lm), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(May_Clon_O3.lm))
```

Residuals for Swords
```{r message = FALSE, warning = FALSE}
# Build the linear model
May_Sword_O3.lm <- lm(`Swords` ~ Year, data = May_O3)

# Create a QQ plot of residuals
qqnorm(residuals(May_Sword_O3.lm))
qqline(residuals(May_Sword_O3.lm), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(May_Sword_O3.lm))
```

## Monthly

May monthly multiplot:
```{r message = FALSE, warning = FALSE}
# Barplot
May_Monthly_O3_plot <- ggplot(May_Monthly_Avgs_O3, aes(x=Year, y=value)) + 
  geom_point(stat="identity",
             size=1) +      # Thinner lines
  geom_errorbar(aes(ymin=value-se, ymax=value+se),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Year',
       y = 'Monthly Avg [O3] µg/m^3',
       color = "Year",
       title = "O3 BAU Averages vs. COVID Average",
       subtitle = "May") + 
  theme_bw()+
  facet_wrap(~ Station, dir = 'v')+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12))
May_Monthly_O3_plot
```

Create separate dataframes for each monitoring station: 
```{r message = FALSE, warning = FALSE}
# Dataframe by station
Rath_Monthly_Avgs_May_O3 <- COVID_Linear_Daily %>%
  filter(Station == "Rathmines (U-B)",
         Month == 5)
Sword_Monthly_Avgs_May_O3 <- COVID_Linear_Daily %>%
  filter(Station == "Swords (S-B)",
         Month == 5)
Clon_Monthly_Avgs_May_O3 <- COVID_Linear_Daily %>%
  filter(Station == "Clonskeagh (S-B)",
         Month == 5)

# Kruskall-wallis test for Rathmines
May_Rath.w <- kruskal.test(value ~ Year, data = Rath_Monthly_Avgs_May_O3)
pairwise.wilcox.test(Rath_Monthly_Avgs_May_O3$value, Rath_Monthly_Avgs_May_O3$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Clonskeagh
May_Clon.w <- kruskal.test(value ~ Year, data = Clon_Monthly_Avgs_May_O3)
pairwise.wilcox.test(Clon_Monthly_Avgs_May_O3$value, Clon_Monthly_Avgs_May_O3$Year,
                 p.adjust.method = "BH")

# Kruskall-wallis test for Swords
May_Sword.w <- kruskal.test(value ~ Year, data = Sword_Monthly_Avgs_May_O3)
pairwise.wilcox.test(Sword_Monthly_Avgs_May_O3$value, Sword_Monthly_Avgs_May_O3$Year,
                 p.adjust.method = "BH")
```

## Weekly

Weekly dataframe:
```{r message = FALSE, warning = FALSE}
# Summary dataframe
Weekly_Avgs_O3 <- summarySE(COVID_Linear_Daily, measurevar= "value", groupvars=c('Station', "Month", "Week", "Year"))

# Make the 'Week' column numerical
Weekly_Avgs_O3$Week <- as.numeric(Weekly_Avgs_O3$Week)

# Filter by month
May_Weekly_Avgs_O3 <- Weekly_Avgs_O3 %>%
  filter(Month == 5)
```

May weekly multiplot:
```{r message = FALSE, warning = FALSE}
# Line plot for weeks
May_Weekly_O3_plot <- ggplot(data = May_Weekly_Avgs_O3, aes(x = Week, y = value)) +
  geom_line(aes(color = Year)) + 
  geom_errorbar(aes(ymin=value-se, ymax=value+se, color = Year),
                size=.3,    # Thinner lines
                width=.2) +
  labs(x = 'Week',
       y = 'Weekly Avg [O3] µg/m^3',
       color = "Year",
       title = "Weekly O3 Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0))
  )
May_Weekly_O3_plot
```

## Daily

Daily averages: 
```{r message = FALSE, warning = FALSE}
# Filter by month
May_Daily_Avgs_O3 <- COVID_Linear_Daily %>%
  filter(Month == 5)

# Make 'Date' column numeric
May_Daily_Avgs_O3$Date <- as.numeric(May_Daily_Avgs_O3$Date)
```

Daily multiplot:
```{r message = FALSE, warning = FALSE}
# Line plot for days
May_Daily_O3_plot <- ggplot(data = May_Daily_Avgs_O3, aes(x = Date, y = value)) +
  geom_line(aes(color = Year)) + 
  geom_errorbar(aes(ymin=value-se, ymax=value+se, color = Year),
                size=.3,    # Thinner lines
                width=.2)+
  labs(x = 'Date',
       y = 'Daily Avg [O3] µg/m^3',
       color = "Year",
       title = "Daily O3 Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0))
  )
May_Daily_O3_plot
```

## Diurnal Analysis

Diurnal weekday analysis:
```{r message = FALSE, warning = FALSE}
# Create weekday dataframe
COVID_Linear_weekday <- COVID_Linear %>%
  filter(weekday >= 1,
         weekday < 6)

# Remove NA values
COVID_Linear_weekday <- COVID_Linear_weekday[!is.na(COVID_Linear_weekday$value), ]

# Remove negative values
COVID_Linear_weekday <- COVID_Linear_weekday %>%
  filter(value >= 0)

# Make 'Year' column a factor
COVID_Linear_weekday$Year <- as.factor(COVID_Linear_weekday$Year)

# Create the two-year average values to compare to the COVID experimental period value. 
COVID_Linear_weekday <- COVID_Linear_weekday %>%
  mutate(Period = case_when(
    Year == '19'| Year =='18' | Year == '17' ~ '2017-2019',
    Year == '20' ~ '2020'))
```

Diurnal weekday averages by year:
```{r message = FALSE, warning = FALSE}
# Weekday summary dataframe
Weekday_Diurnal_Avgs_O3 <- summarySE(COVID_Linear_weekday, measurevar= "value", groupvars=c('Station', "Year", "Month", "Hour" ))

# Make 'Year' column a factor
Weekday_Diurnal_Avgs_O3$Year <- as.factor(Weekday_Diurnal_Avgs_O3$Year)

# Isolate May
May_weekday_Diurnal_Avgs_O3 <- Weekday_Diurnal_Avgs_O3 %>%
  filter(Month == 5)
```

Diurnal May multiplot weekday:
```{r message = FALSE, warning = FALSE}
# Create separate dataframes for each year
May_weekday_Diurnal_Avgs_O3_17 <- May_weekday_Diurnal_Avgs_O3 %>%
  filter(Year == '17')
May_weekday_Diurnal_Avgs_O3_18 <- May_weekday_Diurnal_Avgs_O3 %>%
  filter(Year == '18')
May_weekday_Diurnal_Avgs_O3_19 <- May_weekday_Diurnal_Avgs_O3 %>%
  filter(Year == '19')
May_weekday_Diurnal_Avgs_O3_20 <- May_weekday_Diurnal_Avgs_O3 %>%
  filter(Year == '20')

# Merge dataframes together
May_weekday_Diurnal_Avgs_O3_17_20 <- cbind(May_weekday_Diurnal_Avgs_O3_17, May_weekday_Diurnal_Avgs_O3_18, May_weekday_Diurnal_Avgs_O3_19,May_weekday_Diurnal_Avgs_O3_20)
May_weekday_Diurnal_Avgs_O3_17_20 <- May_weekday_Diurnal_Avgs_O3_17_20[,-c(10:14, 19:23, 28:32)]

# Calculate avg hourly differences
Hryl_diff_O3_17_20_indiv <- May_weekday_Diurnal_Avgs_O3_17_20 %>%
  mutate(hrly_diff_1 = value-value.3,
         hrly_diff_2 = value.1-value.3, 
         hrly_diff_3 = value.2-value.3)
Hryl_diff_O3_17_20_indiv_sum_1 <- summarySE(Hryl_diff_O3_17_20_indiv, measurevar= "hrly_diff_1", groupvars=c('Station'))
Hryl_diff_O3_17_20_indiv_sum_2 <- summarySE(Hryl_diff_O3_17_20_indiv, measurevar= "hrly_diff_2", groupvars=c('Station'))
Hryl_diff_O3_17_20_indiv_sum_3 <- summarySE(Hryl_diff_O3_17_20_indiv, measurevar= "hrly_diff_3", groupvars=c('Station'))

# Line plot of diurnal patterns by year
May_weekday_Diurnal_O3_plot <- ggplot(data = May_weekday_Diurnal_Avgs_O3_17_20, aes(Hour)) +
  geom_line(aes(y = value, group = 1, colour = "2017")) +
  geom_line(aes(y = value.1, group = 1, colour = "2018")) +
  geom_line(aes(y = value.2, group = 1, colour = "2019")) +
  geom_line(aes(y = value.3, group = 1, colour = "2020")) + 
  geom_errorbar(aes(ymin=value-se, ymax=value+se, colour = "2017"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.1-se.1, ymax=value.1+se.1, colour = "2018"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.2-se.2,
                    ymax=value.2+se.2, colour = "2019"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.3-se.3, ymax=value.3+se.3, colour = "2020"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Hour',
       y = 'Hourly Avg [O3] µg/m^3',
       color = "Year",
       title = "Weekday Diurnal O3 Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12)
  )
May_weekday_Diurnal_O3_plot
```

Diurnal weekday averages by period:
```{r message = FALSE, warning = FALSE}
# Weekday summary dataframe
Weekday_period_Diurnal_Avgs_O3 <- summarySE(COVID_Linear_weekday, measurevar= "value", groupvars=c('Station', "Period", "Month", "Hour" ))

# Make 'Year' column a factor
Weekday_period_Diurnal_Avgs_O3$Period <- as.factor(Weekday_period_Diurnal_Avgs_O3$Period)

# Separate May
May_Weekday_period_Diurnal_Avgs_O3 <- Weekday_period_Diurnal_Avgs_O3 %>%
  filter(Month == 5)
```

Diurnal May multiplot weekday:
```{r message = FALSE, warning = FALSE}
# Create separate dataframes for each period
May_Weekday_period_Diurnal_Avgs_O3_17_19 <- May_Weekday_period_Diurnal_Avgs_O3 %>%
  filter(Period == '2017-2019')
May_Weekday_period_Diurnal_Avgs_O3_20 <- May_Weekday_period_Diurnal_Avgs_O3 %>%
  filter(Period == '2020')

# Merge dataframes together
May_Weekday_period_Diurnal_Avgs_O3_17_20 <- cbind(May_Weekday_period_Diurnal_Avgs_O3_17_19,May_Weekday_period_Diurnal_Avgs_O3_20)

May_Weekday_period_Diurnal_Avgs_O3_17_20 <- May_Weekday_period_Diurnal_Avgs_O3_17_20[,-c(10:14)]

# Calculate avg hourly differences
Hryl_diff_O3_17_20 <- May_Weekday_period_Diurnal_Avgs_O3_17_20 %>%
  mutate(hrly_diff = value-value.1)
Hryl_diff_O3_17_20_sum <- summarySE(Hryl_diff_O3_17_20, measurevar= "hrly_diff", groupvars=c('Station'))

# Line plot of diurnal patterns by time period
May_Weekday_period_Diurnal_O3_plot <- ggplot(data = May_Weekday_period_Diurnal_Avgs_O3_17_20, aes(Hour)) +
  geom_line(aes(y = value, group = 1, colour = "2017-2019 Avg")) +
  geom_line(aes(y = value.1, group = 1, colour = "2020")) +
  geom_errorbar(aes(ymin=value-se, ymax=value+se, colour = "2017-2019 Avg"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.1-se.1, ymax=value.1+se.1, colour = "2020"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Hour',
       y = 'Hourly Avg [O3] µg/m^3',
       color = "Time Period",
       title = "Weekday Diurnal O3 Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12)
  )
May_Weekday_period_Diurnal_O3_plot
```

Diurnal weekend dataframe:
```{r message = FALSE, warning = FALSE}
# Create weekend dataframe
COVID_Linear_weekend <- COVID_Linear %>%
  filter(weekday >= 6,
         weekday <= 7)

# Remove NA values
COVID_Linear_weekend <- COVID_Linear_weekend[!is.na(COVID_Linear_weekend$value), ]

# Remove negative values
COVID_Linear_weekend <- COVID_Linear_weekend %>%
  filter(value >= 0)

COVID_Linear_weekend$Year <- as.factor(COVID_Linear_weekend$Year)

# Create the two-year average values to compare to the COVID experimental period value. 
COVID_Linear_weekend <- COVID_Linear_weekend %>%
  mutate(Period = case_when(
    Year == '19'| Year =='18' | Year == '17' ~ '2017-2019',
    Year == '20' ~ '2020'))
```

Diurnal weekend Averages
```{r message = FALSE, warning = FALSE}
# Create summary dataframe
weekend_Diurnal_Avgs_O3 <- summarySE(COVID_Linear_weekend, measurevar= "value", groupvars=c('Station', "Year", "Month", "Hour" ))

# Make 'Year' column a factor
weekend_Diurnal_Avgs_O3$Year <- as.factor(weekend_Diurnal_Avgs_O3$Year)

# Separate May
May_weekend_Diurnal_Avgs_O3 <- weekend_Diurnal_Avgs_O3 %>%
  filter(Month == 5)
```

Diurnal May multiplot weekend:
```{r message = FALSE, warning = FALSE}
# Create separate dataframes for each year
May_weekend_Diurnal_Avgs_O3_17 <- May_weekend_Diurnal_Avgs_O3 %>%
  filter(Year == '17')
May_weekend_Diurnal_Avgs_O3_18 <- May_weekend_Diurnal_Avgs_O3 %>%
  filter(Year == '18')
May_weekend_Diurnal_Avgs_O3_19 <- May_weekend_Diurnal_Avgs_O3 %>%
  filter(Year == '19')
May_weekend_Diurnal_Avgs_O3_20 <- May_weekend_Diurnal_Avgs_O3 %>%
  filter(Year == '20')

# Bind dataframes together
May_weekend_Diurnal_Avgs_O3_17_20 <- cbind(May_weekend_Diurnal_Avgs_O3_17, May_weekend_Diurnal_Avgs_O3_18, May_weekend_Diurnal_Avgs_O3_19,May_weekend_Diurnal_Avgs_O3_20)

May_weekend_Diurnal_Avgs_O3_17_20 <- May_weekend_Diurnal_Avgs_O3_17_20[,-c(10:14, 19:23, 28:32)]

# Calculate avg hourly differences
Hryl_diff_O3_17_20_indiv_weekend <- May_weekend_Diurnal_Avgs_O3_17_20 %>%
  mutate(hrly_diff_1 = value-value.3,
         hrly_diff_2 = value.1-value.3, 
         hrly_diff_3 = value.2-value.3)
Hryl_diff_O3_17_20_indiv_weekend_sum_1 <- summarySE(Hryl_diff_O3_17_20_indiv_weekend, measurevar= "hrly_diff_1", groupvars=c('Station'))
Hryl_diff_O3_17_20_indiv_weekend_sum_2 <- summarySE(Hryl_diff_O3_17_20_indiv_weekend, measurevar= "hrly_diff_2", groupvars=c('Station'))
Hryl_diff_O3_17_20_indiv_weekend_sum_3 <- summarySE(Hryl_diff_O3_17_20_indiv_weekend, measurevar= "hrly_diff_3", groupvars=c('Station'))

# Line plot of weekend averages
May_weekend_Diurnal_O3_plot <- ggplot(data = May_weekend_Diurnal_Avgs_O3_17_20, aes(Hour)) +
  geom_line(aes(y = value, group = 1, colour = "2017")) +
  geom_line(aes(y = value.1, group = 1, colour = "2018")) +
  geom_line(aes(y = value.2, group = 1, colour = "2019")) +
  geom_line(aes(y = value.3, group = 1, colour = "2020")) + 
  geom_errorbar(aes(ymin=value-se, ymax=value+se, colour = "2017"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.1-se.1, ymax=value.1+se.1, colour = "2018"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.2-se.2,
                    ymax=value.2+se.2, colour = "2019"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.3-se.3, ymax=value.3+se.3, colour = "2020"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Hour',
       y = 'Hourly Avg [O3] µg/m^3',
       color = "Year",
       title = "Weekend Diurnal O3 Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12)
  )
May_weekend_Diurnal_O3_plot
```

Diurnal weekend averages by period: 
```{r message = FALSE, warning = FALSE}
# Create weekend summary dataframe by period
weekend_period_Diurnal_Avgs_O3 <- summarySE(COVID_Linear_weekend, measurevar= "value", groupvars=c('Station', "Period", "Month", "Hour" ))

# Make 'Period' a factor
weekend_period_Diurnal_Avgs_O3$Period <- as.factor(weekend_period_Diurnal_Avgs_O3$Period)

# Isolate May
May_weekend_period_Diurnal_Avgs_O3 <- weekend_period_Diurnal_Avgs_O3 %>%
  filter(Month == 5)
```

Diurnal May multiplot weekend:
```{r message=FALSE, warning=FALSE}
# Create separate dataframes for each period
May_weekend_period_Diurnal_Avgs_O3_17_19 <- May_weekend_period_Diurnal_Avgs_O3 %>%
  filter(Period == '2017-2019')
May_weekend_period_Diurnal_Avgs_O3_20 <- May_weekend_period_Diurnal_Avgs_O3 %>%
  filter(Period == '2020')

# Bind dataframes together
May_weekend_period_Diurnal_Avgs_O3_17_20 <- cbind(May_weekend_period_Diurnal_Avgs_O3_17_19,May_weekend_period_Diurnal_Avgs_O3_20)

May_weekend_period_Diurnal_Avgs_O3_17_20 <- May_weekend_period_Diurnal_Avgs_O3_17_20[,-c(10:14)]

# Calculate avg hourly differences
Hryl_diff_O3_17_20_weekend <- May_weekend_period_Diurnal_Avgs_O3_17_20 %>%
  mutate(hrly_diff = value-value.1)
Hryl_diff_O3_17_20_sum_weekend <- summarySE(Hryl_diff_O3_17_20_weekend, measurevar= "hrly_diff", groupvars=c('Station'))

# Create lineplot
May_weekend_period_Diurnal_O3_plot <- ggplot(data = May_weekend_period_Diurnal_Avgs_O3_17_20, aes(Hour)) +
  geom_line(aes(y = value, group = 1, colour = "2017-2019 Avg")) +
  geom_line(aes(y = value.1, group = 1, colour = "2020")) +
  geom_errorbar(aes(ymin=value-se, ymax=value+se, colour = "2017-2019 Avg"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=value.1-se.1, ymax=value.1+se.1, colour = "2020"),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = 'Hour',
       y = 'Hourly Avg [O3] µg/m^3',
       color = "Time Period",
       title = "Weekend Diurnal O3 Patterns",
       subtitle = "May")+
  facet_wrap(~ Station, dir = 'v')+
  theme_bw()+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12)
  )
May_weekend_period_Diurnal_O3_plot
```