---
title: "Mobility Data Analysis"
author: "Henry Perillo"
date: "7/12/2020"
output: html_document
---

This markdown file details the processing and creation of mobility graph from Google COVID-19 mobility datasets.

Load necessary packages:
```{r message = FALSE, warning = FALSE}
# Clear working environment:
rm(list = ls())

# Load Packages
library(dplyr)
library(plyr)
library(readr)
library(Hmisc)
library(psych)
library(rmweather)
library(ranger)
library(hexbin)
library(tidyr)
library(stringr)
library(ggplot2)
library(data.table)
library(lubridate)
library(Rmisc)
library(knitr)
```

Import dataset:
```{r message = FALSE, warning = FALSE}
# Set working directory
setwd("~/Desktop/Research_Project/Data/AQ/Preliminary_Data")

# Call file
mobility <- read_csv('Global_Mobility_Report.csv')
```

Create dataframe:
```{r message = FALSE, warning = FALSE}
# Isolate necessary rows
mobility <- mobility %>%
  filter(country_region == 'Ireland',
         sub_region_1 == 'County Dublin')

# Turn 'date' column into Date format
mobility <- mobility %>%
  mutate(date = gsub('/', '-', date))
mobility$date <- as.Date(mobility$date, tryFormats = c("%m-%d-%y"))

# Rename columns
mobility <- mobility %>%
  dplyr::rename(Retail = retail_and_recreation_percent_change_from_baseline,
         Grocery = grocery_and_pharmacy_percent_change_from_baseline,
         Parks = parks_percent_change_from_baseline,
         Transit = transit_stations_percent_change_from_baseline,
         Workplace = workplaces_percent_change_from_baseline,
         Residential = residential_percent_change_from_baseline)
```

Make figure for entire lockdown period:
```{r message = FALSE, warning = FALSE}
# Mobility lineplot
Mobility_plot <- ggplot(data = mobility, aes(x = date))+
  geom_line(aes(y = Retail, group = 1, colour = "Retail"))+
  geom_line(aes(y = Grocery, group = 1, colour = "Grocery"))+
  geom_line(aes(y = Parks, group = 1, colour = "Parks"))+
  geom_line(aes(y = Transit, group = 1, colour = "Transit"))+
  geom_line(aes(y = Workplace, group = 1, colour= "Workplace"))+
  geom_line(aes(y = Residential, group = 1, colour = "Residential"))+
  labs(x= 'Date',
       y = '% Change from Baseline',
       title = "Mobility Changes During COVID Lockdown",
       subtitle = "Co. Dublin",
       color = "Sector")+
  geom_vline(xintercept=as.numeric(mobility$date[c(26)]),
             linetype=2, colour="black")+
  geom_hline(yintercept = 0, linetype = 1, colour = "black")+
  theme_bw()
Mobility_plot
```

Create time period column and attain averages for each time period:
```{r message = FALSE, warning = FALSE}
# Create 'Month,' 'Year,' and 'Date' columns
mobility <- mobility %>%
  mutate(Year = str_sub(date,3,4),
         Month = str_sub(date,6,7),
         Date = str_sub(date,9,10))

# Add 'Period' column
mobility <- mobility  %>% 
  mutate(Period = case_when(
    Month == '02' ~ 'Before Lockdown',
    Month == '03' & Date < 11 ~ 'Before Lockdown', 
    Month == '03' & Date > 10 ~ 'During Lockdown',
    Month > '03' ~ 'During Lockdown'))

# Turn 'mobility' into a factor
mobility$Period <- as.factor(mobility$Period)

# Re-format data frame
mobility_se <- mobility %>%
  gather('Retail', 'Parks', 'Grocery', 'Transit', 'Workplace', 'Residential', key = "Sector", value = '% Change from BAU')
```

Examine differences between weekdays and weekends:
```{r message = FALSE, warning = FALSE}
# Make 'date' column as.POSIXct
mobility_se$date <- lubridate::parse_date_time(mobility_se$date, "%Y-%m-%d")

# Obtain 'weekday' columns 
mobility_se <- mobility_se %>% 
  dplyr::rename(value = '% Change from BAU') %>%
  rmw_prepare_data(na.rm = TRUE)

# Isolate May
may_mobility <- mobility_se %>%
  filter(Month == '05')

# Identify weekdays and weekends
may_mobility <- may_mobility %>%
  mutate(`Day_Type` = case_when(
    weekday <= 5 ~ 'Weekday',
    weekday >= 6 ~ 'Weekend'))

# Create summary dataframe for graphing
mobility_may <- summarySE(may_mobility,
                          measurevar= 'value',
                          groupvars=c('Sector', "Day_Type"))
```

May multiplot for mobility between weekdays and weekends: 
```{r message = FALSE, warning = FALSE}
# Barplot
multi_may_mobility <- ggplot(mobility_may, aes(x=Day_Type, y= `value`)) + 
  geom_point(stat="identity",
             size=1) +      # Thinner lines
  geom_errorbar(aes(ymin=value-se, ymax=value+se),
                size=.3,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x = "Days",
       y = "% Change from BAU",
       title = "Weekdays vs. Weekends",
       subtitle = "Mobility Changes by Sector") + 
  theme_bw()+
  facet_wrap(~ Sector, dir = 'v')+
  theme(
    strip.text.x = element_text(margin = margin(2, 0, 2, 0), size = 12))
multi_may_mobility
```

Analyze differences between weekdays and weekends: 
```{r}
# Get 'Weekday' column
mobility$date <- lubridate::parse_date_time(mobility$date, "%Y-%m-%d")
mobility <- mobility %>% 
  dplyr::rename(value = 'Retail') %>%
  rmw_prepare_data(na.rm = TRUE)

# Separate weekdays and weekends
mobility <- mobility %>%
  mutate(`Day_Type` = case_when(
    weekday <= 5 ~ 'Weekday',
    weekday >= 6 ~ 'Weekend'))

# Isolate the month of May
mobility_in_May <- mobility %>%
  filter(Month == '05')
```


## Tests for Normality: 

Retail: 
```{r message = FALSE, warning = FALSE}
# Build the linear model
Retail_model_day <- lm(value ~ Day_Type, data = mobility_in_May)
# Create a QQ plot of residuals
qqnorm(residuals(Retail_model_day))
qqline(residuals(Retail_model_day), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(Retail_model_day))
```

Grocery: 
```{r message = FALSE, warning = FALSE}
# Build the linear model
Grocery_model_day <- lm(Grocery ~ Day_Type, data = mobility_in_May)
# Create a QQ plot of residuals
qqnorm(residuals(Grocery_model_day))
qqline(residuals(Grocery_model_day), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(Grocery_model_day))
```

Parks: 
```{r message = FALSE, warning = FALSE}
# Build the linear model
Parks_model_day <- lm(Parks ~ Day_Type, data = mobility_in_May)
# Create a QQ plot of residuals
qqnorm(residuals(Parks_model_day))
qqline(residuals(Parks_model_day), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(Parks_model_day))
```

Workplace: 
```{r message = FALSE, warning = FALSE}
# Build the linear model
Workplace_model_day <- lm(Workplace ~ Day_Type, data = mobility_in_May)
# Create a QQ plot of residuals
qqnorm(residuals(Workplace_model_day))
qqline(residuals(Workplace_model_day), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(Workplace_model_day))
```

Transit: 
```{r message = FALSE, warning = FALSE}
# Build the linear model
Transit_model_day <- lm(Transit ~ Day_Type, data = mobility_in_May)
# Create a QQ plot of residuals
qqnorm(residuals(Transit_model_day))
qqline(residuals(Transit_model_day), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(Transit_model_day))
```

Residential: 
```{r message = FALSE, warning = FALSE}
# Build the linear model
Residential_model_day <- lm(Residential ~ Day_Type, data = mobility_in_May)
# Create a QQ plot of residuals
qqnorm(residuals(Residential_model_day))
qqline(residuals(Residential_model_day), col = "red")

# Shapiro-wilk test
shapiro.test(residuals(Residential_model_day))
```

Statistics:
```{r message = FALSE, warning = FALSE}
# Non-parametric wilcoxon tests
grocery_day.t <- t.test(Grocery ~ Day_Type, data = mobility_in_May)
grocery_day.t

workplace_day.t <- t.test(Workplace ~ Day_Type, data = mobility_in_May)
workplace_day.t

parks_day.t <- t.test(Parks ~ Day_Type, data = mobility_in_May)
parks_day.t

transit_day.t <- t.test(Transit ~ Day_Type, data = mobility_in_May)
transit_day.t
```
